---
title: "ELF Multivariate Analysis"
output: word_document
---

```{r include = FALSE, warning = FALSE}
library(pander)
base_url <- 'http://deq2.bse.vt.edu/d.dh'
options(timeout=2000);
library('gdata')
source("/var/www/R/config.local.private");
source(paste(base_directory,"Analysis/query_elf_statistics.R", sep = "/")); 
bundle <- 'watershed';
ftype <- 'nhd_huc8';
metric <- 'aqbio_nt_total';
selected <- 'all';
quantile <- 0.8;
analysis_timespan = "full";
sampres = "species";
dataset_tag = 'bpj-530'; # bpj-530, bpj-rcc, 'HUC8_quantregwHuc6bp' (huc 6)
q_ftype <- 'fe_quantreg_ymax'; # fe_quantreg, fe_quantreg_pwit, fe_quantreg_ymax, fe_twopoint
pmax  <- 0.15;

data = fn_dh_elfstats (
    ftype = q_ftype,
    site = base_url,
    analysis_timespan = analysis_timespan,
    yvar = metric,
    sampres = sampres, # e.g. species, e.
    stat_quantreg_qu = quantile, # upper quantile to use
    feature_ftype = ftype,
    #stat_quantreg_ghi = stat_quantreg_ghi, #
    #stat_quantreg_glo = stat_quantreg_glo, # use 1 for pwit, 0 for quantreg
    dataset_tag = dataset_tag
);

data.da <- subset(data, in_xvar == 'nhdp_drainage_sqmi');
data.mean <- subset(data, in_xvar == 'erom_q0001e_mean');
data.jan <- subset(data, in_xvar == 'erom_q0001e_jan');
data.feb <- subset(data, in_xvar == 'erom_q0001e_feb');
data.mar <- subset(data, in_xvar == 'erom_q0001e_mar');
data.apr <- subset(data, in_xvar == 'erom_q0001e_apr');
data.may <- subset(data, in_xvar == 'erom_q0001e_may');
data.jun <- subset(data, in_xvar == 'erom_q0001e_june');
data.jul <- subset(data, in_xvar == 'erom_q0001e_july');
data.aug <- subset(data, in_xvar == 'erom_q0001e_aug');
data.sep <- subset(data, in_xvar == 'erom_q0001e_sept');
data.oct <- subset(data, in_xvar == 'erom_q0001e_oct');
data.nov <- subset(data, in_xvar == 'erom_q0001e_nov');
data.dec <- subset(data, in_xvar == 'erom_q0001e_dec');
n = c('DA', 'Mean', 'January', 'February', 'March', 'April', 'May', 'June', 'July', 'August', 'September', 'October', 'November', 'December')
title <- paste("R^2 of upper ", 100.*(1.0 - quantile), "% for \n", metric, " = f(DA), f(Qmean), f(Qjan),..., f(Qdec) for ", ftype);
```
* Location: `r selected`
* quantile: `r quantile`
* Metric: `r metric`
* Geospatial Unit: `r ftype`
* Analysis Type: `r qftype`

```{r }
boxplot(
  data.da$out_rsq_adj, data.mean$out_rsq_adj, data.jan$out_rsq_adj, data.feb$out_rsq_adj, data.mar$out_rsq_adj, 
  data.apr$out_rsq_adj, data.may$out_rsq_adj, data.jun$out_rsq_adj, data.jul$out_rsq_adj, data.aug$out_rsq_adj, 
  data.sep$out_rsq_adj, data.oct$out_rsq_adj, data.nov$out_rsq_adj, data.dec$out_rsq_adj,
  names = n, 
  main = title
);

# box-whisker plot of breakpoint by y-metric (biometric)

```{r }
title <- paste("Breakpoint summary for \n", metric, " = f(DA), f(Qmean), f(Qjan),..., f(Qdec) for ", ftype);
boxplot(
  data.da$out_breakpoint, data.mean$out_breakpoint, data.jan$out_breakpoint, data.feb$out_breakpoint, data.mar$out_breakpoint, 
  data.apr$out_breakpoint, data.may$out_breakpoint, data.jun$out_breakpoint, data.jul$out_breakpoint, data.aug$out_breakpoint, 
  data.sep$out_breakpoint, data.oct$out_breakpoint, data.nov$out_breakpoint, data.dec$out_breakpoint,
  names = n, 
  main = title
);
z <- cbind(
  as.matrix(summary(data.da$out_breakpoint)), 
  as.matrix(summary(data.mean$out_breakpoint)), 
  as.matrix(summary(data.jan$out_breakpoint)), 
  as.matrix(summary(data.may$out_breakpoint)), 
  as.matrix(summary(data.aug$out_breakpoint)), 
  as.matrix(summary(data.dec$out_breakpoint))
)
colnames(z) <- c('DA', 'Mean', 'January', 'April', 'August', 'December')
pander(z)
```